### 2023-09-14 manuscript.tex
We provide multiple notebooks [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/c89de3aab786e55c724102ed14dbb33fb23561e5.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/c89de3aab786e55c724102ed14dbb33fb23561e5/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/6187161665

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...1dcd4ef07da5b54f4e19c12f8df6e68aaf709e51\#files_bucket}{is further updated} since re-submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/1dcd4ef07da5b54f4e19c12f8df6e68aaf709e51/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/1dcd4ef07da5b54f4e19c12f8df6e68aaf709e51}{habi/EAWAG-manuscript@1dcd4ef}
on September 14, 2023.

@@

The presented method offers an insight and algorithm on how to perform tomographic scans, preview and analyze micro-computer tomographic datasets of a large collection of fish.
The workflow is relying only on free and open-source software and can thus be used and verified independently by any interested reader.
All the \emph{Jupyter} notebook described herein is also freely available online {[}\protect\hyperlink{ref-1HteOscVd}{19}{]}.

>>>>

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...c89de3aab786e55c724102ed14dbb33fb23561e5\#files_bucket}{is further updated} since re-submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/c89de3aab786e55c724102ed14dbb33fb23561e5/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/c89de3aab786e55c724102ed14dbb33fb23561e5}{habi/EAWAG-manuscript@c89de3a}
on September 14, 2023.

@@

The presented method offers an insight and algorithm on how to perform tomographic scans, preview and analyze micro-computer tomographic datasets of a large collection of fish.
The workflow is relying only on free and open-source software and can thus be used and verified independently by any interested reader.
All the \emph{Jupyter} notebooks described herein are also freely available online {[}\protect\hyperlink{ref-1HteOscVd}{19}{]}.
